--- 
title: "ND110 - Data Science I - Notebook"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Course Info {-}

<h4>Tags</h4>

* Author       : AH Uyekita
* Dedication   : 10 hours/week (suggested)
* Start        : 14/12/2018
* End (Planned): 28/12/2018
* Title        : Data Science I - Foundations Nanodegree Program
    * COD      : ND110

<h4>Related Courses</h4>

* [ND110 - Data Science I - Nanodegree Foundations][nd110]

[nd110]: https://br.udacity.com/course/python-fundamentos-data-science--nd110

***************************************************************************************************

<h2>Objectives</h2>

I want to finish this course in two weeks. It includes the Optional videos and chapters.

<h2>Syllabus</h2>

* [x] Chapter 1 - Welcome
    * [x] Lesson 01 -
    * [x] Lesson 02 -
* [x] Chapter 2 - Python Introduction
    * [x] Lesson 01 -
    * [x] Lesson 02 -
    * [x] Lesson 03 -
    * [x] Lesson 04 -
    * [x] Lesson 05 -
* [x] Chapter 3 - Python for Data Analysis
    * [x] Lesson 01 -
    * [x] Lesson 02 -
    * [x] Lesson 03 -
    * [x] Lesson 04 -

<h3>Repository Structure</h3>

This is the structure of this repository, each course's chapters (or parts) will be stored in different folders.

```
ND110_data_science_foundation_01
|
+--  01-Chapter_01
|           |
|           +--  README.md                       # General information
|
+--  02-Chapter_02
|           |
|           +--  README.md                       # General information
|           +--  00-Project_01                   # Project 01
|           +--  01-Lesson_01                    # Files from Lesson 01
|           |        +--  README.md              # Notes from Lesson 01 from Chapter 02
|           +--  02-Lesson_02                    # Files from Lesson 02
|           |        +--  README.md              # Notes from Lesson 02 from Chapter 02
|           .
|
+--  03-Chapter_03
|           |
|           +--  README.md                       # General information
|           +--  00-Project_02                   # Project 02
|           +--  01-Lesson_01                    # Files from Lesson 01
|           |        +--  README.md              # Notes from Lesson 01 from Chapter 02
|           +--  02-Lesson_02                    # Files from Lesson 02
|           |        +--  README.md              # Notes from Lesson 02 from Chapter 02
|           .
```

<h3>Best practice</h3>

* Add all _deliverables_ in the [`GitKraken Glo`][bp_1];
* Take notes using the [`Markdown`][bp_2].

[bp_1]: https://www.gitkraken.com/invite/5Ua2spL4
[bp_2]: https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(.packages(), 'bookdown', 'knitr', 'rmarkdown'), 'packages.bib')
```

```{r,message=FALSE,include=FALSE}
# Saving the original Work Directory
original_wd <- getwd()

# Goes to the parents level (\docs) - Where the files will be rendered
setwd('..')

# Creating a list of all html files.
rm_html <- list.files(pattern = c('*.html'))

# Cleaning the \docs, removing all html files.
file.remove(rm_html)

# Saving the \docs path
destino <- getwd()

# Returning to original path
setwd(original_wd)

# Defining _book as work directory
setwd('_book')

# List of files to be copied
html_files_folders <- list.files()

# Copying the files from _books to \docs folder
file.copy(html_files_folders, to = destino, overwrite = TRUE, recursive = TRUE)

# Defining the original Work Directory
setwd(original_wd)
```